discussion

### 2018-05-15 man/ms_3_discussion.Rmd
update text

@@

El sitio del norte, ()

@@

@@

* Quizá estamos asumiendo que es una población marginal, pero sin embargo lo es solamente geográficamente
")
```

@@

* Vicente-Serrano: 
    * We found that some forests from cold and humid areas respond to shorter drought time-scales than forests from dry areas, which usually respond to longer time-scales
    * Growth and responses to drought are modulated by site conditions such as soil type, specific functional traits and the intensity of competition among neighbouring trees (Orwig & Abrams, 1997; McDowell et al., 2008; Linares et al., 2010; Pasho et al., 2011).
    * Our findings provide evidence that the patterns of growth response to drought do not follow a general geographical structure and that these patterns are driven by the biogeographical, topographic and climatic conditions of each site, showing that forests located in different continents have the same pattern of response to drought time-scales.

>>>>

Our results showed differences for greenness and tree-growth between northern and southern oak populations (Table 3). Las poblaciones del norte, que presentan condiciones mas secas (Tabla 1), se vieron mas afectadas por los eventos de sequía. Así por ejemplo vimos que las anomalías estandarizadas de EVI fueron mas negativas en la población del norte durante la sequía de 2005 (mayor intensidad de browing en 2005 para el norte).

A striking result is the difference for tree growth between sites (Figure 4). The trees of CA-High site, which are located around 1900 m. a.s.l. and representing the upper limit of the treeline of the species in this southernmost location, showed higher BAI than those located at low-elevations sites (CA-Low and SJ) (Figure 4). This is especially interesting for southern sites, which are very close to each other. Our results are consistent with previous findings that pointed out tree growth and tree responses to drought are site-dependent (e.g. soil features, tree competence, etc.) [e.g. @Babst2013, @VicenteSerrano2014b], particularly for rear-edge populations [@Cavin2017, @Dorado2017c].

When we explored the chracteristics of the southern sites, we firstly observed a difference in elevation. @Bhuyan2017, in a recent work across the European continent, found a clearly effect of elevation on the resistance to drought of several tree-species, where stands located at higher elevations were less drought sensitive. The higher values of tree growth that we observed in CA-High site could be related with lower water stress at high-elevation sites, since moisture availability is a key factor limiting tree growth for *Q. pyrenaica* [@GeaIzquierdo2014]. In fact, the differences in available water of soils could explain our results. [@CoboDiaz2017], who studied microbiota of this location in an elevational gradient, found higher values of available water of the forest soils located on high elevation compared with those located at low elevations. In this sense, a remarkably observation supporting this idea, is the presence of a traditional irrigation ditches located uphill from the CA-High site. In most of the high-mountain watersheds of Sierra Nevada, there is a system of historical irrigation channels, know as *acequias de careo*, that was used since Middle Age to cultivated these valleys [@MartinCivantos2014, @MartinCivantos2016]. These ditches run through the hillsides of valleys releasing water through several points that filtrate the water to recharge the aquifer and then irrigates the foot of the slopes [@MartinCivantos2014, @Jodar2017]. There is a ditch (*Acequia de la Era Alta*) located uphill the CA-High site, which functions from March to June [@RuizRuiz2017]. It brings water from snowmelt and from a nearby stream, soaking the *Q. pyrenaica* forests. 
Finally another idea to consider is the different degree of anthropic impact related to elevation.

Aunque nuestros sitios presenten valores similares de competencia, la historia de manejo humano puede ser diferente, y en parte se relaciona con la altitud. Así en zonas altas encontramos un menor impacto humano que en las zonas bajas. Esto ocurre

Another reason that could explain the higher values of BAI of CA-High site is el grado diferente de impacto antrópico. En nuestros resultados vemos como los bosques situados a mayor altitud presentan un menor impacto antrópico. Esto puede ser simplemente por el hecho de que estos bosques estén menos accesibles ---> ojo y la idea de que son bosque relativamente jóvenes 
---> Gráfica 
Our sampled sited showed similar tree competence levels (Table 1), but ... impacto antrópico diferente

* Quizá están creciendo donde les están dejando (menor impacto antrópico en las zonas mas altas, al menos en los últimos años??)

The presence of *Q. pyrenaica* forests on the southern slopes of Sierra Nevada is partly explained by the additional contribution of humid air from the Mediterranean sea [@Prieto1975]

```{r echo=FALSE, results='asis', eval=show_text}
cat("
* Vicente-Serrano: 
    * We found that some forests from cold and humid areas respond to shorter drought time-scales than forests from dry areas, which usually respond to longer time-scales
    * Growth and responses to drought are modulated by site conditions such as soil type, specific functional traits and the intensity of competition among neighbouring trees (Orwig & Abrams, 1997; McDowell et al., 2008; Linares et al., 2010; Pasho et al., 2011).
    * Our findings provide evidence that the patterns of growth response to drought do not follow a general geographical structure and that these patterns are driven by the biogeographical, topographic and climatic conditions of each site, showing that forests located in different continents have the same pattern of response to drought time-scales.

-----------

@@

------

")

```

@@

* Quizá estamos asumiendo que es una población marginal, pero sin embargo lo es solamente geográficamente

-----

@@

In addition, despite southern sites are very close to each other, we obtained higher values of BAI for the high-elevation site than for the low-elevation site.

@@
